Title-- \today{}

### 2019-11-25 article.tex

\journal{Journal of Computational Physics}

@@

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:

\title{Robust calibration of numerical models based on relative regret}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author[vt]{Victor Trappler}
\ead{victor.trappler@univ-grenoble-alpes.fr}
\author[ea]{Élise Arnaud}
\author[av]{Arthur Vidard}
\author[ld]{Laurent Debreu}

\address[vt]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP*, LJK, 38000 Grenoble, France}

\begin{abstract}
%% Text of abstract
Classical methods of parameter estimation usually imply the minimisation of an objective function, that measures the error between some observations and the results obtained by a numerical model. In the presence of random inputs, the objective function becomes a random variable, and notions of robustness have to be introduced.

In this paper, we are going to present how to take into account those uncertainties by defining a notion of robustness based on the distribution of the conditional minimisers and compare it with the minimum in the mean sense, and the minimum of variance.
\end{abstract}

% %%Graphical abstract
% \begin{graphicalabstract}
% %\includegraphics{grabs}
% \end{graphicalabstract}

%%Research highlights
% \begin{highlights}
% \item Research highlight 1
% \item Research highlight 2
% \end{highlights}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section*{Introduction}
\label{}

@@

The model we wish to calibrate is based on the Shallow Water equations, described Eq.~\eqref{eq:SWE_equations}. $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant. The parameter to calibrate, $\mathbf{k}$, is the quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient. The environmental parameter $\mathbf{u}$ is the amplitude of a sine wave of period $1/\omega_0$. The domain of those two parameters are $\mathcal{K} = [0.0, 1.3]$ and $\mathcal{U} = [0.5, 0.7]$.

\begin{align}
  \label{eq:SWE_equations}
  \left\{
    \begin{array}{rl}
      \partial_t h + \partial_x q &= 0 \\
      \partial_t q + \partial_x \left(\frac{q^2}{h} + \frac{g}{2}h^2\right) &= - gh\partial_x z - \mathbf{k}q |q|h^{-7/3} \\
      h(0, t) &= 20.0 + 3\cdot \sin \left(\frac{2\pi t}{2}\right) + 1.5\cdot \mathbf{u} \cdot \sin\left(\frac{2 \pi t}{\omega_0}\right)\\
      \partial_x q(0, t) &= 0
      \end{array}
  \right.
\end{align}
These equations are integrated using a finite-volume scheme on a discretized domain $[0, L]$, up to a time $T$. The output of the computer code is the sea surface height $h$, on the center of all the volumes and at all the time-steps, that will be denoted $\mathcal{M}(\mathbf{k},\mathbf{u};\, \omega_0=1.0)$.
In this setting, the variable input is uniformly distributed on $\mathcal{U}$.
To generate the observations, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}}; \, \omega_0 = 0.999)$. $\omega_0$  
represents here the uncontrollable error between the observations and the numerical model and will now be omitted systematically in the notation. The true value of the bottom friction $\mathbf{k}^{\mathrm{true}} = (k_1^{\mathrm{true}}, k_2^{\mathrm{true}},\dots, k_{N_\mathrm{vol}}^{\mathrm{true}})$ is not constant over the whole domain, and is defined as
\begin{equation*}
{k}^{\mathrm{true}}_i = 0.2\cdot \left(1 + \sin\left(\frac{2 \pi x_i}{L}\right)\right)
\end{equation*}
where $x_i$ is the center of the $i$-th volume. The two sources of representativity errors are $\omega_0$, and the fact that we are looking to estimate $\mathbf{k}$ in a 1-dimensional space $\Kspace$. 
\subsection{Estimation}
Given that the numerical model is expensive to evaluate, it has first been evaluated on a relatively small regular grid. A metamodel based on Gaussian process is constructed and the PEI criterion~\citep{ginsbourger_bayesian_2014,bossek_learning_2015} allow us to add point to evaluate and to better capture the locus of the conditional minimisers $\{(\mathbf{k}^*(\mathbf{u}), \mathbf{u}) \mid \mathbf{u} \in \Uspace \}$. A bigger regular grid is evaluated by the metamodel once the design space has been sufficiently explored. The different steps of the estimation are illustrated Figure~\ref{fig:estimation_swe}. We can see that the estimation for this problem seems less problematic than the analytical examples shown above, as all derived quantites are unimodal.
The different estimates however take a wide range of values, as seen on Table~\ref{tab:recap_estimates_metaSWE}. As a basis for comparison, the global minimiser of $J$ over $\Kspace \times \Uspace$ has been computed, and $\kest_{\mathrm{global}}$ is then obtained by discarding the $\mathbf{u}$ value.

@@

\begin{figure}[!h]
\centering
\includegraphics[width=.7\textwidth]{Figures/RobustSWEmis_plots.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:estimation_swe}
\end{figure}
\begin{table*}[!h]
\centering
\caption{Calibrated values of $\mathbf{k}$ according to different criteria}
\begin{tabular}{lr} \toprule
Estimator & Value \\ \midrule
$\hatkmpe$ & 0.249 \\
$\kest_{\mathrm{global}}$ & 0.290 \\
$\hatkp,~p=1$ & 0.423 \\ 
$\hatkp,~p=0.90$ & 0.458 \\ 
$\hatkmean$ & 0.501 \\ 
$\hatkp,~p=0.80$ & 0.505 \\ 
$\hatkp,~p=0.70$ & 0.560 \\ 
$\hatkvar$ & 0.990\\ \bottomrule
\end{tabular}
\label{tab:recap_estimates_metaSWE}
\end{table*}
Similarly as for $\JBH$ and $\JBHS$, the profiles are depicted Figure~\ref{fig:profiles_swe}.
\begin{figure}[!h]
  \centering
  \includegraphics[width=.8\textwidth]{Figures/profile_swe}
  \caption{Profiles for the calibration problem}
\label{fig:profiles_swe}
\end{figure}
We can see that the performances of $\kest_1$ and $\hatkmean$ are very similar, but $\kest_1$ has better performances when $\mathbf{u} > 0.6$. When comparing with the global optimiser $\kest_{\mathrm{global}}$, $\kest_1$ performs better when $\mathbf{u}<0.625$. As $\mathbf{U}$ is uniformly distributed on $\Uspace=[0.5,0.7]$, we can graphically estimate that the probability that $\kest_1$ outperforms $\kest_{\mathrm{global}}$ is greater than $0.5$, that is that $\Prob_\mathbf{U}\left[J(\kest_1,\mathbf{U})<J(\kest_{\mathrm{global}},\mathbf{U})\right] > 0.5$.

The calibration of this numerical model is done in order to get a calibrated value $\kest$, that will be used for forecasts, using the same numerical model. We are now going to compare how well three of those values compare in a forecast context: $\kest_1$, $\hatkmean$ and $\kest_{\mathrm{global}}$, as the first two refer quite naturally to the notion of robustness, and the latter is an example of an estimate that does not take into account the uncertainties.
\clearpage
\subsection{Assessing the quality of the forecast of the calibrated model}
The calibration of the model has been performed using by integrating the model on a time-period $[0, T]$, called assimilation window. 
We now want to compare the quality of the different forecasts, from different calibrated bottom friction.
Those forecasts result from the integration of the numerical model between the time $T$ and a time $T_{\mathrm{pred}}$.

Given the probabilistic nature of the environmental conditions $\mathbf{U}$, the forecasts will also be probabilistic. We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, for a calibrated $\mathbf{k}$.

\subsubsection{Squared forecast error}
Given two environmental conditions $\mathbf{u}$, used to run the computer simulation and $\mathbf{u}'$, used to generate the observations, the squared forecast error for the parameter $\mathbf{k}$ is
\begin{equation}
\label{eq:squared_forecast_error}
S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}
Averaging over $\mathbf{u}$, $\mathbf{u}'$ defines the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps. This can be done using a Monte-Carlo approximation: as $\mathbf{u}$ and $\mathbf{u}'$ are iid, let us assume that we have a set of samples $\{\mathbf{u}^i\}_{1\leq i \leq N_{\mathbf{u}}}$. 
\begin{equation}
  \label{eq:squared_forecast_error_averaged}
  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}}^2 }\sum_{i=1}^{N_{\mathbf{u}}}\sum_{j=1}^{N_{\mathbf{u}}} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u}^i,\mathbf{u}^j) = \frac{1}{N_{\mathbf{u}}^2 }\sum_{i=1}^{N_{\mathbf{u}}}\sum_{j=1}^{N_{\mathbf{u}}}  \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}^i) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}^j)\right)^2
\end{equation}
The mean squared forecast error averaged over the whole space and over all the time-steps gives an indication on the overall prediction quality of the prediction given this metric, and are represented on the right plot of Figure~\ref{fig:forecast_squared_error}. We can see that $\kest_{\mathrm{global}}$ performs slightly better than $\kest_1$, itself performing slightly better than $\hatkmean$.
Averaging $S(\mathbf{\kest}$ over only the time steps between $T$ and $T_{\mathrm{pred}}$, we have an indication on the quality of the forecast in the squared sense depending on the spatial position, as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
\begin{figure*}[!h]
\centering
\includegraphics[width=.9\textwidth]{Figures/forecast_error.pdf}
\caption{Quality of forecast, depending on the calibrated parameter. The left figures show the metric averaged over time, while the right figure show the mean forecast error, averaged over time and space}
\label{fig:forecast_squared_error}
\end{figure*}
We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.
\begin{figure}[!h]
  \centering
  \includegraphics[width=.9\textwidth]{Figures/forecast_CRPS}
  \caption{CRPS computed for different calibrated parameters}
\label{fig:forecast_crps}
\end{figure}

@@

\subsubsection{Continuous Ranked Probability Score}
Given the random variables $\mathcal{M}_{\mathrm{pred}}(\kest, \mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$, representing the probabilistic forecast and the probabilistic observations, we can define the cumulative distribution functions (CDF) $F_{\mathrm{pred}}(\cdot, \kest)$ and $F^o_{\mathrm{pred}}(\cdot)$
The Continuous ranked probability score (CRPS) measures the squared difference between the predicted CDF $F_{\mathrm{pred}}$ using a calibrated value, and the CDF of the observations $F_{\mathrm{pred}}^o$. 
\begin{equation}
\label{eq:def_crps}
\mathrm{CRPS}(\mathbf{k}) = \int_{\mathbb{R}} (F_{\mathrm{pred}}(x,\mathbf{k}) - F^o_{\mathrm{pred}}(x))^2 \,\mathrm{d}x
\end{equation}

>>>>

@@

\title{Title-- \today{}}%TEXT}

% \Author[affil]{given_name}{surname}

\Author[]{Victor}{Trappler}
\Author[]{Élise}{Arnaud}
\Author[]{Laurent}{Debreu}
\Author[]{Arthur}{Vidard}

\affil[]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP*, LJK, 38000 Grenoble, France}
% \affil[]{ADDRESS}

%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.

\runningtitle{Title}

\runningauthor{Trappler V.}

\correspondence{Victor Trappler (victor.trappler@univ-grenoble-alpes.fr)}

\received{}
\pubdiscuss{} %% only important for two-stage journals
\revised{}
\accepted{}
\published{}

%% These dates will be inserted by Copernicus Publications during the typesetting process.

\firstpage{1}

\maketitle

% \listoftodos\

\begin{abstract}
Classical methods of parameter estimation usually imply the minimisation of an objective function, that measures the error between some observations and the results obtained by a numerical model. In the presence of random inputs, the objective function becomes a random variable, and notions of robustness have to be introduced.

In this paper, we are going to present how to take into account those uncertainties by defining a notion of robustness based on the distribution of the conditional minimisers and compare it with the minimum in the mean sense, and the minimum of variance.
\victor{Pour le nom: Il y a l'idée que l'on veut avoir un regret $J(\mathbf{k},\mathbf{u}) - \alpha J^*(\mathbf{u})$ controlé à l'aide de $\alpha$: Relative regret ?}
\end{abstract}

\copyrightstatement{TEXT}

@@

The model we wish to calibrate is based on the Shallow Water equations, described Eq.~\eqref{eq:SWE_equations}. $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant. The parameter to calibrate, $\mathbf{k}$, is the quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient. The environmental parameter $\mathbf{u}$ is the amplitude of a sine wave of period $1$. The domain of those two parameters are $\mathcal{K} = [0.0, 1.3]$ and $\mathcal{U} = [0.5, 0.7]$.

\begin{align}
  \label{eq:SWE_equations}
  \left\{
    \begin{array}{rl}
      \partial_t h + \partial_x q &= 0 \\
      \partial_t q + \partial_x \left(\frac{q^2}{h} + \frac{g}{2}h^2\right) &= - gh\partial_x z - \mathbf{k}q |q|h^{-7/3} \\
      h(0, t) &= 20.0 + 3\cdot \sin \left(\frac{2\pi t}{2}\right) + 1.5\cdot \mathbf{u} \cdot \sin\left(2 \pi t\right)\\
      \partial_x q(0, t) &= 0
      \end{array}
  \right.
\end{align}
These equations are integrated using a finite-volume scheme on a discretized domain $[0, L]$, up to a time $T$. The output of the computer code is the sea surface height $h$, on the center of all the volumes and at all the time-steps, that will be denoted $\mathcal{M}(\mathbf{k},\mathbf{u})$.
In this setting, the variable input is uniformly distributed on $\mathcal{U}$.
To generate the observations, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}})$. 
This true value $\mathbf{k}^{\mathrm{true}} = (k_1^{\mathrm{true}}, k_2^{\mathrm{true}},\dots, k_{N_\mathrm{vol}}^{\mathrm{true}})$ is not constant over the whole domain, and is defined as
\begin{equation*}
{k}^{\mathrm{true}}_i = 0.2\cdot \left(1 + \sin\left(\frac{2 \pi x_i}{L}\right)\right)
\end{equation*}
where $x_i$ is the center of the $i$-th volume.
\subsection{Estimation}
Given that the numerical model is expensive to evaluate, it has first been evaluated on a relatively small regular grid. A metamodel based on Gaussian process is constructed and the PEI criterion~\citep{ginsbourger_bayesian_2014,bossek_learning_2015} allow us to add point to evaluate and to better capture the locus of the conditional minimisers $\{(\mathbf{k}^*(\mathbf{u}), \mathbf{u}) \mid \mathbf{u} \in \Uspace \}$. A bigger regular grid is evaluated by the metamodel once the design space has been sufficiently explored. The different steps of the estimation are illustrated Figure~\ref{fig:estimation_swe}. We can see that the estimation for this problem seems less problematic than the analytical examples shown above, as all derived quantites are unimodal.
The different estimates however take a wide range of values, as seen on Table~\ref{tab:recap_estimates_metaSWE}. As a basis for comparison, the global minimiser of $J$ over $\Kspace \times \Uspace$ has been computed, and $\kest_{\mathrm{global}}$ is then obtained by discarding the $\mathbf{u}$ value.

@@

\begin{figure}[!h]
\centering
\includegraphics[width=.7\textwidth]{Figures/RobustSWEmis_plots.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:my_label}
\end{figure}
\begin{table*}[!h]
\centering
\caption{Calibrated values of $\mathbf{k}$ according to different criteria}
\begin{tabular}{lr} \toprule
Estimator & Value \\ \midrule
$\hatkmpe$ & 0.249 \\
$\kest_{\mathrm{global}}$ & 0.290 \\
$\hatkp,~p=1$ & 0.423 \\ 
$\hatkp,~p=0.90$ & 0.458 \\ 
$\hatkmean$ & 0.501 \\ 
$\hatkp,~p=0.80$ & 0.505 \\ 
$\hatkp,~p=0.70$ & 0.560 \\ 
$\hatkvar$ & 0.990\\ \bottomrule
\end{tabular}
\caption{Estimation of $\mathbf{k}$ according to different criterion}
\label{tab:recap_estimates_metaSWE}
\end{table*}
Similarly as for $\JBH$ and $\JBHS$, the profiles are depicted Figure~\ref{fig:profiles_swe}.
\begin{figure}[!h]
  \centering
  \includegraphics[width=.8\textwidth]{Figures/profile_swe}
  \caption{Profiles for the calibration problem}
\label{fig:profiles_swe}
\end{figure}
We can see that the performances of $\kest_1$ and $\hatkmean$ are very similar, but $\kest_1$ has better performances when $\mathbf{u} > 0.6$. When comparing with the global optimiser $\kest_{\mathrm{global}}$, $\kest_1$ performs better when $\mathbf{u}<0.625$. As $\mathbf{U}$ is uniformly distributed on $\Uspace=[0.5,0.7]$, we can graphically estimate that the probability that $\kest_1$ outperforms $\kest_{\mathrm{global}}$ is greater than $0.5$, that is that $\Prob_\mathbf{U}\left[J(\kest_1,\mathbf{U})<J(\kest_{\mathrm{global}},\mathbf{U})\right] > 0.5$.

The calibration of this numerical model is done in order to get a calibrated value $\kest$, that will be used for forecasts, using the same numerical model. We are now going to compare how well three of those values compare in a forecast context: $\kest_1$, $\hatkmean$ and $\kest_{\mathrm{global}}$, as the first two refer quite naturally to the notion of robustness, and the latter is an example of an estimate that does not take into account the uncertainties.
\clearpage
\subsection{Assessing the quality of the forecast of the calibrated model}
The calibration of the model has been performed on the time-period $[0, T]$, called assimilation window. 
We now want to compare the quality of the different forecasts depending on the criterion used to calibrate the bottom friction.
To define those forecasts, the models will be integrated from $T$ to $T_{\mathrm{pred}}$.

Given the probabilistic nature $\mathbf{U}$, the forecasts will also be probabilistic. We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, for a calibrated $\mathbf{k}$.

\subsubsection{Squared forecast error}
Let us assume that the observations result from the parameter $\mathbf{u}'$, while the computer simulation is run using $\mathbf{u}$.
The squared forecast error given $\mathbf{u}$ and $\mathbf{u}'$ is
\begin{equation}
\label{eq:squared_forecast_error}
S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}
Averaging over $\mathbf{u}$, $\mathbf{u}'$ defines the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps. This can be done using a Monte-Carlo approximation: as $\mathbf{u}$ and $\mathbf{u}'$ are iid, let us assume that we have a set of samples $\{\mathbf{u}^i\}_{1\leq i \leq N_{\mathbf{u}}}$. 
\begin{equation}
  \label{eq:squared_forecast_error_averaged}
  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}}^2 }\sum_{i=1}^{N_{\mathbf{u}}}\sum_{j=1}^{N_{\mathbf{u}}} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u}^i,\mathbf{u}^j) = \frac{1}{N_{\mathbf{u}}^2 }\sum_{i=1}^{N_{\mathbf{u}}}\sum_{j=1}^{N_{\mathbf{u}}}  \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}^i) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}^j)\right)^2
\end{equation}
The mean squared forecast error averaged over the whole space and over all the time-steps gives an indication on the overall prediction quality of the prediction given this metric, and are represented on the right plot of Figure~\ref{fig:forecast_squared_error}. We can see that $\kest_{\mathrm{global}}$ performs slightly better than $\kest_1$, itself performing slightly better than $\hatkmean$.
Averaging $S(\mathbf{\kest}$ over only the time steps between $T$ and $T_{\mathrm{pred}}$, we have an indication on the quality of the forecast in the squared sense depending on the spatial position, as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
\begin{figure*}[!h]
\centering
\includegraphics[width=.9\textwidth]{Figures/L2_full.pdf}
\caption{Quality of forecast, depending on the calibrated parameter. The left figures show the metric averaged over time, while the right figure show the mean forecast error, averaged over time and space}
\label{fig:forecast_squared_error}
\end{figure*}
We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.
\begin{figure}[!h]
  \centering
  \includegraphics[width=.9\textwidth]{Figures/CRPS_full}
  \caption{CRPS computed for different calibrated parameters}
\label{fig:forecast_crps}
\end{figure}

@@

\subsubsection{Continuous Ranked Probability Score}
Given the random variables $\mathcal{M}_{\mathrm{pred}}(\kest, \mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$, representing the probabilistic forecast and the probabilistic observations, we can define the cumulative distribution functions (CDF) $F_{\mathrm{pred}}(\cdot, \kest)$ and $F^o_{\mathrm{pred}}(\cdot)$
The Continuous ranked probability score (CRPS) measures the squared difference between the predicted CDF $F_{\mathrm{pred}}$ using a calibrated value, and the CDF of the observations $F_{\mathrm{pred}}^o$. 
\begin{equation}
\label{eq:checkloss}
\rho_{\tau}(x) = \begin{cases}
    \tau |x| \quad \text{ if } x \geq 0 \\
    (1- \tau) |x| \quad \text{ if } x < 0
\end{cases}
\end{equation}

Given the time index $j$, and the volume indexed by $i$, the quantile of order $\tau\in [0, 1]$ of $\mathcal{M}(\kest, \mathbf{U})_{(i,j)}$ is $q_{(i,j)}(\tau)$.
Given an obse
\begin{figure*}[t]
\includegraphics[width=12cm]{Figures/forecast_metric.pdf}
\caption{Quality of forecast, depending on the calibrated parameter. The left figures show the metric averaged over time, while the right figures show}
\label{fig:forecast_metric}
\end{figure*}

% \subsection{The Lorenz-63 model}
% A classical toy problem in data assimilation is the Lorenz-63 model, introduced in \cite{lorenz_deterministic_1963}. 
% % xb
% The evolution of the state vector $(x,y,z)$ is described by the non-linear differential system of Eq.~\eqref{eq:lorenz_equations}
% \begin{align}
%   \label{eq:lorenz_equations}
%   \left\{
%     \begin{array}{l}
%       \dot{x} = \sigma\left(y-x \right) \\
%       \dot{y} = \rho x - y - xz \\
%       \dot{z} = xy - \beta z
%       \end{array}
%   \right.
% \end{align}
% Despite its apparent simplicity, this system is known to show chaotic behaviour for $(\sigma,\rho,\beta) = (10, 28, 8/3)$. 
% This differential system is solved numerically using a Runge-Kutta scheme, over $N=100$ time-steps of length $\Delta t = 0.05$. In that time-period, the chaotic behaviour is not yet too apparent.

% The inputs of the computer code are the initial conditions $\left(x_0,y_0,z_0\right)$ and $(\sigma, \beta, \rho)$. The parameter to calibrate is $\mathbf{k}=x_0-1$ with $\mathbf{k}\in[-0.05,0.05]$, and the uncertain parameter is $\mathbf{u}=\beta - 8/3$ with $\mathbf{u} \in \Uspace=[-0.05, 0.05]$. Finally, we suppose that the random variable $\mathbf{U}$ follows an uniform distribution on $\Uspace$. Solving numerically the differential system using those settings yields $x_{i}(\mathbf{k},\mathbf{u})$ for $i$ between $1$ and $N$.

% This problem of calibration will be studied in a twin experiments framework: the target state $x^{o}_i$ for $1\leq i \leq N$ has been generated by the computer code, where the parameters used to generate it are detailed in Table~\ref{tab:lorenz_modelling}. One can notice the discrepancy of $\rho$ between the observations and the model, introduced to ensure that no perfect fit can be achieved, for any set of parameters. 
% \begin{table*}[h]
%   \caption{Choice of modelling of the Lorenz-63 system}
%   \label{tab:lorenz_modelling}
% \begin{tabular}{crrl}
%   \tophline
%   Parameter & Observation: $x_{1:N}^o$ & Modelling: $\mathcal{G}(\mathbf{k},\mathbf{u})$ & Type \\
%   \middlehline
%  $\sigma$ & $10$ & $10$ & Fixed\\
%   $\rho$ & $29$ & $28$ & A priori chosen and fixed \\
%   $\beta$ & ${8}/{3}$ & ${8}/{3} + \mathbf{u}$ & A priori chosen and uncertain \\
%  $x_0$ & $1$ & $1 + \mathbf{k}$ & Calibrated \\
%   $y_0$ & $0$ & $0$ & Fixed \\
%  $z_0$ & $0$ & $0$ & Fixed \\
%   \bottomhline
% \end{tabular}
% \end{table*}

% The misfit between the observations and the output of the numerical model is quantified using the cost function:
% \begin{equation}
% \label{eq:cost_fun_lorenz}
% J(\mathbf{k},\mathbf{u}) = \frac{1}{2}\|\mathcal{G}(\mathbf{k},\mathbf{u}) \|^2 = \frac{1}{2} \|x_{1:N}(\mathbf{k},\mathbf{u}) - x^o_{1:N} \|^2 = \frac{1}{2}\sum_{i=1}^N (x_i(\mathbf{k},\mathbf{u}) - x_i^o)^2
% \end{equation}

% This toy model is cheap to evaluate, so the global minimum can be computed using numerical methods, at different starting points to avoid local minimums.
% \begin{equation}
% \label{eq:min_global_lorenz}
% \min_{(\mathbf{k},\mathbf{u}) \in \Kspace\times\Uspace} J(\mathbf{k},\mathbf{u}) = 38.886712815 \quad \argmin_{(\mathbf{k},\mathbf{u}) \in \Kspace\times\Uspace} J(\mathbf{k},\mathbf{u}) = (0.02414384, -0.00551042)
% \end{equation}

% \subsubsection{MPE and conditional moments}
% Figure~\ref{fig:lorenz_kde_moments} shows the cost function $J$, computed on a regular grid over $\Kspace\times\Uspace$. Using this grid, the conditional mean and standard deviation have been computed, while the MPE has been estimated by KDE. For a single $\mathbf{u}$, it may appear that there are multiple $\mathbf{k}^*(\mathbf{u})$. This is due to the fact that the conditional minimiser jumps back and forth between the two curves.

% \begin{figure}[!h]
% \includegraphics[width=12cm]{Figures/lorenz_kde_moments.pdf}
% \caption{Cost function, locus of conditional minimisers, MPE estimated with KDE, conditional moments and their associated estimates}
% \label{fig:lorenz_kde_moments}
% \end{figure}

% \subsubsection{Relaxation of the constraint}
% Based on the computations described before, the coefficient $\checkap$ have been computed for $p=0.9$, $0.95$ and $p=1$, and reported in Table~\ref{tab:recap_estimates_lorenz}. The curve $R_{\checka_1}$ is plotted in Figure~\ref{fig:lorenz_relax}, where the acceptable region for $\checka_1$ is filled in yellow.

% \begin{figure}[!h]
% \includegraphics[width=12cm]{Figures/lorenz_f3.pdf}
% \caption{Relaxation of the constraint for the Lorenz model. Acceptable region in yellow}
% \label{fig:lorenz_relax}
% \end{figure}

% We can see that for $\mathbf{k}$ being approximately between $0$ and $0.01$, the probability $R_{\checka_1}$ is very close to $1$. Indeed, the cost function seems to be relatively flat on this region, as $\checkk_{0.9} \approx \kmpe$.

% \begin{table*}[!h]
%   \caption{Estimates computed numerically on the Lorenz-63 model}
%   \label{tab:recap_estimates_lorenz}
%   \begin{tabular}{*{3}{r}}\tophline
%     Estimate & Value & Related quantities\\
%     \middlehline
%     $\hatkmean$        & $ 0.008779$ &$\left(\mu(\kmean),\sigma(\kmean)\right) = (42.965, 4.921)$\\
%     $\hatkvar$         & $-0.025338$ &$\left(\mu(\kvar),\sigma(\kvar)\right)= (50.704, 2.024)$\\
%     $\hatkmpe$         & $ 0.008779$ & $\Gamma_1(\kmpe) = 0.053$ \\
%     $\hat{\checkk}_{0.9}$ & $ 0.008729$ & $\hat{\checka}_{0.9}  = 1.202788$ \\
%     $\hat{\checkk}_{0.95}$& $ 0.006078$ & $\hat{\checka}_{0.95} = 1.226050$ \\
%     $\hat{\checkk}_{1}$   & $ 0.000275$ & $\hat{\checka}_{1}    = 1.311002$ \\
%     \bottomhline
%     \end{tabular}
% \end{table*}

% \subsubsection{Selection of the couple $(p,\checkap)$}
% The evolution of $\checkap$ with respect to $p$ is shown on the left plot of Figure~\ref{fig:evolution_p_lorenz}. We can see that $\checkap$ presents two abrupt positive change of slope, for $p$ set to $0.85$ and just before $1$. Those confidence levels corresponds to the local maxima of the ratio $p/\checkap$, that is shown on the right plot of Figure~\ref{fig:evolution_p_lorenz}. The profile of $\checkk_{0.85}$ corresponding to the local maximum of the ratio, has not been plotted as it corresponds to the same profile of $\kmean$.

% \begin{figure*}[!h]
% \includegraphics[width=12cm]{Figures/evol_p_lorenz.pdf}
% \caption{Evolution of $p$ and $\checkap$}
% \label{fig:evolution_p_lorenz}
% \end{figure*}
% In order to compare the values taken by the objective function, the profiles have been represented on Figure~\ref{fig:lorenz_profiles}.
% \begin{figure}[!h]
% % \includegraphics[width=12cm]{Figures/lorenz_cdf_profile.pdf}
% \includegraphics[width=12cm]{Figures/profile_lorenz_all_estimates.pdf}
% \caption{Profiles of different $\mathbf{k}$ for the Lorenz model}
% \label{fig:lorenz_profiles}
% \end{figure}
% The profile of $\kmean$ presents a good insight on the performances of this estimate: for most values of the uncertain variables, the objective is low. In contrast, for $\mathbf{u}$ close to $0.05$, a maximum is reached. 
%\begin{figure}[!h]
%\includegraphics[width=8.3cm]{Figures/cdf_lorenz_with_ratio.pdf}
%\caption{CDF corresponding to different $\mathbf{k}$ for the Lorenz model}
%\label{fig:lorenz_cdf}
%\end{figure}

% \clearpage
% \subsection{Context: Shallow water equations and bottom friction}

% The quality of water circulation modelling in coastal areas is largely dependent on the boundary conditions, (e.g.\ the tide), the bathymetry and the friction induced by the rugosity of the ocean bed \citep{boutet_estimation_2015}. The latter will then be estimated in a robust manner, by applying the criteria introduced above.

% The model studied is based on the one-dimensional shallow water equations, described Eq.~\eqref{eq:SWE_equations}, solved numerically on a domain $D$. $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant. $\mathbf{k}$ is a quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient.
% \begin{align}
%   \label{eq:SWE_equations}
%   \left\{
%     \begin{array}{l}
%       \partial_t h + \partial_x q = 0 \\
%       \partial_t q + \partial_x \left(\frac{q^2}{h} + \frac{g}{2}h^2\right) = - gh\partial_x z - \mathbf{k}q |q|h^{-7/3} \\
%       h(0, t) = 20.0 + \mathrm{Amplitude} \cdot \sin \left(\frac{2\pi}{\mathbf{u}}t\right) \\
%       q(0, t) = 0
%       \end{array}
%   \right.
% \end{align}
